---
title: "Course Summary"
author: "Song Yao"
date: "October 21, 2016"
output: html_document
---

## Day 1: Packages and Version Control

We learned to create a package using [devtools][1]. The way to get started is to create the skeleton of a package.

```
library(devtools)
create("pkg")
```

This creates a directory with a couple of files and a folder. We then did the following:

1. The DESCRIOTION file contains info about the package; we edited it for our purposes.
2. We looked at the NAMESPACE, but didn't touch it.
3. We created our first function in the R folder, `hi()`.

We then used [roxygen2][] to add documentation to the function, including information about parameters and return values. We also used tags (`@export`) to indicate that we wanted to export the function from the NAMESPACE. 

We also learned to manage source code using [github][].

Here's the result of our work:
```{r our-package}
library(pkg)
hi("Martin")
```

## Day 2: Classic, Rich, and Tidy data

'Classic' data is represented as a `data.frame()` with samples as rows and features as columns. 

```{r}
pdatafl <- "/Users/yao/Dropbox/Office/Rlearning/Intermediate.R/pkg/ALL-phenoData.csv"
exprfl <- "/Users/yao/Dropbox/Office/Rlearning/Intermediate.R/pkg/ALL-expression.csv"
classic <- input_classic(pdatafl, exprfl)
classic[1:3, c(1:3, 22:24)]
```

One of the things we did was to plot the distribution of expression valuse across genes.

```{r classic-exprs}
hist(colMeans(classic[, -(1:22)]))
```

[1]: https://cran.r-project.org/package=devtools
[roxygen2]: https://cran.r-project.org/package=roxygen2
[github]: https://github.com/
